Neural dialogue act recognition with transformer pre-training

### 2019-04-06 abstract.tex
add diagram

\documentclass[11pt,a4paper,headings=standardclasses]{scrartcl}

\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{hyperref}
\usepackage{natbib}

@@

However, given that BERT is pre-trained on book and encyclopedia data, 
there is no guarantee that the representations it learns will improve performance on dialogue-specific tasks.
Adding that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
To assess BERT's for dialogue applications, we propose a series of DAR experiments that BERT to encode utterances, 
which are fed to simple RNN to predict sequences of dialogue acts.
In particular, we are interested in whether BERT can be fine-tuned to adequately represent
dialogue-specific features such as discourse markers, disfluency, and laughter.

@@

>>>>

\documentclass[11pt,a4paper,headings=standardclasses]{article}

\usepackage[margin=1in]{geometry}
\usepackage{url}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{tikz}
\usepackage[bf]{caption}

@@

However, given that BERT is pre-trained on book and encyclopedia data, 
there is no guarantee it will improve performance on dialogue-specific tasks.
Adding to that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
To assess BERT's potential for dialogue applications, we propose a series of DAR experiments 
with various utterance encoders, including BERT.
Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts.
In particular, we are interested in whether BERT can be fine-tuned to adequately represent
dialogue-specific features such as discourse markers, disfluency, and laughter.

@@

\input{architecture-diagram.tex}
